Modeling Environmental Stochasticity

### 2022-04-21 notes/environmental stochasticity.Rmd
format notes

```{r data, echo=TRUE}
tar_load(data_full)
```

@@

library(patchwork)
p0 + p1 + p2 + p3 & labs(y = ".fitted") & theme(legend.position = "none") & plot_annotation(title=  "survival probability")
```

>>>>

```{r data, echo=TRUE}
withr::with_dir(here(), tar_load(data_full))
```

@@

library(patchwork)
p0 + p1 + p2 + p3 &
  labs(y = ".fitted") &
  theme(legend.position = "none") &
  plot_annotation(title = "survival probability")
```
